The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd
Create function to get tf-idf statistic

```{r}
#| label: tf-idf

emu_theses_words

emu_theses_words_count <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  ungroup()

emu_theses_words_total <- emu_theses_words_count |> 
  group_by(title) |> 
  summarise(total = sum(n))

emu_theses_words_count <- left_join(emu_theses_words_count, emu_theses_words_total)

# emu_theses_words_count |> 
#   group_by(title) |> 
#   summarise(total = unique(tot

# Preview term frequency distributions in a subset of theses
ggplot(emu_theses_words_count |> 
         filter(title == unique(title)[1:6]),
       aes(n/total, fill = title)) +
  geom_histogram(show.legend = FALSE, binwidth = 0.0001) +
  xlim(NA, 0.0009) +
  facet_wrap(~ title, ncol = 3, scales = "free_y")

# Examine Zipf's law for the EMU theses
## Calculate rank and term frequency
freq_by_rank <- emu_theses_words_count |> 
  group_by(title) |> 
  mutate(rank = row_number(),
         `term frequency` = n/total)

@@

## Calculate tf-idf
emu_theses_words_count <- emu_theses_words_count |> 
  bind_tf_idf(word, title, n)
emu_theses_words_count

emu_theses_words_count |> 
  select(-total) |> 
  arrange(desc(tf_idf))

>>>>

The `tf-idf` statistic shows words that are the most important to one document in a collection of documents [@silge2017]. In this case, it shows high values for the names of thesis locations that tend to be high-frequency thesis-specific words.

```{r tf-idf}
## Calculate tf-idf statistic
emu_theses_tf_idf <- emu_theses_words |> 
  get_tf_idf(title_col = "title", word_col = "word")

## Get top n words most specific to each thesis 
emu_theses_tf_idf |> 
  group_by(title) |> 
  top_n(5, tf_idf) |> 
  arrange(desc(tf_idf), .by_group = TRUE)
```

```{r}
# Preview term frequency distributions in a subset of theses
ggplot(emu_theses_words_count |> 
         filter(title == unique(title)[1:6]),
       aes(n/total, fill = title)) +
  geom_histogram(show.legend = FALSE, binwidth = 0.0001) +
  xlim(NA, 0.0009) +
  facet_wrap(~ title, ncol = 3, scales = "free_y")
```

```{r}
# Examine Zipf's law for the EMU theses
## Calculate rank and term frequency
freq_by_rank <- emu_theses_words_count |> 
  group_by(title) |> 
  mutate(rank = row_number(),
         `term frequency` = n/total)

@@
